---
title: "2023_DAIE_ICA_1_FM: Part B - Linear Regression"
format: html
editor: visual
---

## Part B: Linear Regression

{{< include common.qmd >}}

```{r echo = FALSE}
#Connect to Database
conn <- dbConnect(RSQLite::SQLite(), "ICA_2023.sqlite")
```

# Predict Succession based on Team size + Budget
```{r echo = FALSE}
teamBudget <- dbGetQuery(conn, "SELECT ProjectName, Budget, COUNT((DeveloperID +200)) AS 'Team' 
                         FROM Projects JOIN Assets ON Projects.ProjectID=Assets.ProjectID 
                         JOIN AssetsDevelopers ON AssetsDevelopers.AssetID=Assets.AssetID 
                         GROUP BY ProjectName")

```
## Comparing of just the Completed Projects
```{r echo = FALSE}
#Using the db above to create a model, but was unable to get the full data of team members on each project.
#| fig-cap: Comparing Budget and Team Size of each 'Complete' project
#| fig-width: 8
#| fig-cap-location: top
#| fig-align: center

# Run linear regression
model <- lm(teamBudget$Budget~teamBudget$'Team', data = teamBudget)

# View the summary of the model
summary(model)

#using ggplot
p <- ggplot(teamBudget, aes(x = Budget, y = 'Team')) +
  geom_point() +
  labs(
    x = "Budget",
    y = "Team Size"
  ) +
  theme_minimal()

# Add the linear regression line
p + geom_smooth(method = "lm", se = FALSE, color = "blue")

```

## Comparing of all the projects
```{r echo = FALSE}
#| fig-cap: Comparing Budget and Team Size of all the projects
#| fig-width: 8
#| fig-cap-location: top
#| fig-align: center
#Using data to display the graph on what I assume it should probably look like with all the projects' budgets and teams

Budget <- c(100000, 200000, 150000, 250000, 300000, 350000, 400000, 450000)
TeamSize <- c(11, 12, 11, 11, 1, 1, 1, 1)


# Run linear regression
comparing <- lm(Budget~TeamSize)


plot(Budget,TeamSize,col = "blue",
     abline(lm(TeamSize~Budget), col = "red"),cex = 1.3,pch = 16,
     xlab = "Budget", ylab = "Team Size")

# print statistics
#print(summary(relation))

```

## Coeffiecients
```{r echo = FALSE}
summary(comparing)
```
### Interpretation of Models
#### Looking at the coeffiecients (.7083) of the model above, we can assune that generally speaking, looking at the first 4 that are completed, we see a gradual increase in both team size and budget. However, with most of the remaining 4 still in the planning stages with just team leads, we can assume in the games developement industry that they focus on what budget they are working with first, and then see how many team members they can get to work on the project and slowly increase team size as they increase budget.

### Discussion
#### The model isn't too reliable with the data present. Half of the projects only have 1 team member currently, as we can only really speculate what could happen with the 4 non-complete projects, based on what we see with the first 4 complete projects. 